HerMES: Spatially resolved ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-01-22 LaTeX/ms.tex
Rob Ivison comments

%\topmargin -0.0in
\def\boldsymbol{\bf}
\newcommand{\tnm}{\tablenotemark}
\newcommand{\tnt}{\tablenotetext}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
    indicates that 36 of the ALMA sources experience a significant flux boost
    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
    and show multiple images.  We introduce and make use of {\sc uvmcmcfit}, a
    general purpose and publicly available Markov Chain Monte Carlo visibility
    plane analysis tool to analyze the source properties.  Nearly 70\% of the
    {\it Herschel} sources break down into multiple ALMA counterparts,
    consistent with previous research indicating that the multiplicity rate is
    high in bright sources discovered in sub-mm or FIR surveys with poor
    spatial resolution.  The ALMA counterparts to our {\it Herschel} targets
    are located much closer to each other than ALMA counterparts to sources
    found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
    underpredict the excess in number of sources with small separations from
    each other that is seen in our ALMA sample.  Combined with our previous
    work on brighter {\it Herschel} sources, the lens models presented here
    constrain the shape of the intrinsic luminosity function for DSFGs to have
    a break around 8$\,$mJy with a very steep fall off at higher flux
    densities.  The high multiplicity rate and low projected separations
    between sources seen in our sample argue in favor of interactions and
    mergers driving the prodigious emission from the brightest DSFGs.

@@

Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimieter
(sub-mm) wavelengths are generally known as dusty star-forming galaxies
(DSFGs).  They cover a wide range in redshift from $z \sim 0.5$ to $z > 6$
\citep{2005ApJ...622..772C, Casey:2012qy, Messias:2014fk, Riechers:2013lr},
with a significant component at $z \sim 2$ \citep{Casey:2012uq,
Bothwell:2013lr}, when they represent the most FIR-luminous objects in
existence during this epoch.   They are signposts of significant over-densities
\citep{Daddi:2009qy, Capak:2011qy} and likely represent
the formative stages of the most massive elliptical galaxies found in the local
Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.  Moreover, they constitute
an important component of the overall galaxy population at $z \sim 2$
\citep[e.g.,][]{Magnelli:2011ul}, when the star-formation rate density in
the Universe peaked \citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.

Our collective understanding of DSFGs is currently taking a dramatic leap
forward thanks in large part to the advent of the {\it Herschel Space
Observatory} \citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has resulted in
a revolution in the size and depth of blind surveys at FIR and sub-mm
wavelengths.  In particular, the {\it Herschel} Multi-tiered Extragalactic
Survey \citep[HerMES;][]{Oliver:2012lr} and the {\it Herschel} Astrophysical
Terahertz Large Area Survey \citep[H-ATLAS;][]{2010PASP..122..499E} together
have surveyed $\approx 650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and
500$\,\mu$m to the confusion limit of {\it Herschel} \citep[$\sigma \approx
6-7\,$mJy in each band][]{Nguyen:2010fk}, plus an additional $\approx
350\,$deg$^2$ to a level approximately double the confusion limit.  A similar
effort to survey large areas of the sky has been undertaken at longer
wavelengths by the South Pole Telescope \citep[SPT;][]{Carlstrom:2011qy} and
the Atacama Cosmology Telescope \citep{Swetz:2011qy}.

@@

\caption{ {\it Herschel}/SPIRE photometry of all galaxies in the H-ATLAS
phase~I catalog with S/N$ > 3$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m
(grayscale).  The sample of HerMES sources in this paper are shown with green
squares (the ``ALMA sample'').  The very bright {\it Herschel} DSFGs from
\citet{Bussmann:2013lr} (the ``SMA sample'') are shown by red circles, and the
overall sample of candidate lensed {\it Herschel} DSFGs are highlighted by
yellow circles.  Lensed SMGs discovered by the SPT that have published lens
models are represented by cyan stars \citep{Hezaveh:2013fk}.  A magenta diamond
shows the location in this diagram of the stacked signal from ALESS DSFGs.
Representative error bars are shown in the lower left corner.  The ALMA sample
fills the gap in 500$\,\mu$m flux density space between SMA/SPT and ALESS
samples.} \label{fig:sample}

@@

ALMA data were obtained during Cycle~0 over a period from 2012 June to 2012
December (Program 2011.0.00539.S; PI: D. Riechers).  The observations were
carried out in good 870$\,\mu$m weather conditions which resulted in typical
system temperatures of $T_{\rm sys} \sim 130\,$K and phase fluctuations of $\sim
10\,$deg.  Each target was observed until an rms noise level of $\sigma \approx
0.2\,$mJy was achieved.  This typically required 10 minutes of on-source
integration time.  For the observations targeting the CDFS, Elais-S, and COSMOS
fields, the weather was of sufficient quality to reach $\sigma \approx
0.14\,$mJy.  The number of antennas used varied from 15 to 25.  The antennas
were configured with baseline lengths of 20$\,$m to 400$\,$m, providing a
synthesized beamsize of $\approx 0\farcs45$ FWHM while ensuring that no flux was
resolved out by the interferometer (since our targets all have size scales
smaller than $1-2 \arcsec$.  When possible, track-sharing of multiple
targets in a single track was used to optimize the {\it uv} coverage.

@@

All observations were conducted with the correlator in ``Frequency Domain
Mode'', providing a total usable bandwidth of 7.5$\,$GHz with spectral windows
centered on 335.995$\,$GHz, 337.995$\,$GHz, 345.995$\,$GHz, 347.996$\,$GHz.  We
searched for evidence of serendipitous spectral lines but found none (typical
sensitivity is $\sigma \approx 8\,$mJy$\,$beam$^{-1}$ in 15$\,$km$\,$sec$^{-1}$
bins).

We used the Common Astronomy Software Applications (CASA, version 4.2.1)
package to investigate the quality of the reduced data provided by the North
American ALMA Science Center (NAASC).  Overall, the quality of the processed
data from the NAASC was very high.  We achieved a significant improvement in
the case of the ADFS and XMM targets by excluding datasets with moderate
$T_{\rm sys}$ and poor phase fluctuations.  For a handful of targets with peak
signal-to-noise ratio (S/N) greater than 20, we obtained a $\approx 10\%$
improvement in S/N by using the CASA {\sc selfcal} task to improve the phase
gain corrections.  Finally, we updated the absolute flux calibration to use the
Butler-JPL-Horizons 2012 solar system models.

@@

Figure~\ref{fig:imaging} presents our ALMA images (colorscale) in comparison to
the {\it Herschel} SPIRE images (black-white contours) originally used to
select the targets and noted in each panel as either 250$\,\mu$m or
350$\,\mu$m.  Each panel is centered on the phase center of the ALMA
observations of that target and a white circle traces the FWHM of the primary
beam of an ALMA 12$\,$m antenna at 870$\,\mu$m.  A white dashed box represents
the region of each image that is shown in greater detail in
Figure~\ref{fig:uvmodels}.

@@

Optical imaging observations using the Gemini Multi-Object Spectrograph-South
\citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of the
program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
structure at $z<1$ and determine which of the ALMA sources are affected by
gravitational lensing.  Nearly half of the ALMA sources lie in regions with
existing deep optical imaging thanks to the extensive HerMES multi-wavelength
dataset --- these were excluded from our Gemini-S program.  The remaining
targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01, HADFS11,
HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each of these
targets were observed for a total of 9$\,$minutes of on-source integration time
in each of $u$, $g$, $r$, $i$, and $z$.  The observations were obtained during
dark time in with adequate seeing conditions (image quality $ = 85\% \approx
1.1\arcsec$.

@@

\caption{ ALMA 870$\mu$m images (color scale, units of mJy/beam) of HerMES
DSFGs.  Contours (black and white) trace 250$\,\mu$m emission from {\it
Herschel}.  The FWHM size of the ALMA synthesized beam is shown in the lower
left corner of each panel.  A solid white circle shows the FWHM size of the
primary beam.  Dashed squares identify the regions of each image that are shown
in greater detail in Figure~\ref{fig:uvmodels}.  \label{fig:imaging}}
\addtocounter{figure}{-1}

@@

When an intervening galaxy (or group of galaxies) is present along the line of
sight, {\sc uvmcmcfit} accounts for the deflection of light caused by this
structure using a simple ray-tracing routine that is adopted from a Python
routine written by A.~Bolton
\footnote{http://www.physics.utah.edu/$\sim$bolton/python\_lens\_demo/}.  This
represents a significant difference from \citet{Bussmann:2012lr} and
\citet{Bussmann:2013lr}, where we used the publicly available {\sc Gravlens}
software \citep{Keeton:2001lr} to map emission from the source plane to the
image plane for a given lensing mass distribution.  {\sc Gravlens} has a wide
range of lens mass profiles as well as a sophisticated algorithm for mapping
source-plane emission to the image-plane, but it also comes with a significant
input/output penalty that makes parallel computing prohibitively expensive.
For example, modeling a simple system comprising one lens and one source
typically required 24-48$\,$hours using the old software, whereas the same
system can be modeled in less than one hour with the pure-Python code.  The use
of pure-Python code for tracing the deflection of light rays is a critical
component of making {\sc uvmcmcfit} computationally feasible.

@@

We use uniform priors for all model parameters.  The prior on the position of
the lenses covers $\pm0\farcs6$ ($1\farcs0$) in both RA and Dec, a value that
reflects the 1-$\sigma$ absolute astrometric solution between the ALMA and
optical/near-IR images of $0\farcs2$ ($0\farcs4$) for SDSS-based (2MASS-based)
astrometric calibration.  In section~\ref{sec:objectbyobject}, we discuss the
level of agreement between the astrometry from the images and the astrometry
from the lens modeling on an object-by-object basis.  For $\theta_{\rm E}$, the
prior covers $0\farcs1 - 6\arcsec$.  The axial ratios of the lenses and sources
are restricted to be $q_{\rm lens} > 0.3$ and $q_{\rm s} > 0.2$. No prior is
placed on the position angle of the lens or source.  The intrinsic flux density
for any source is allowed to vary from 0.1$\,$mJy to the total flux density
observed by the ALMA (we ensure that the posterior PDF of the intrinsic flux
density shows no signs of preferring a value lower than 0.1$\,$mJy).  The source
position is allowed to vary over any reasonable range necessary to fit the data
(typically, this is $\pm 1-2\arcsec$).  The effective radius is allowed to vary
from $0\farcs01 - 1\farcs5$.

@@

{\bf HXMM07:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy detected in the Gemini-S image.  There is a $\approx
0\farcs5$ offset in the position of the foreground galaxy between the lens
model and the Gemini-S image.  Given the absolute astrometric uncertainty of
$0\farcs2$ (based on SDSS), we do not consider this offset to be significant.
The presence of a handful of $\pm3\sigma$ peaks in the residual map is likely
an indication that our assumption of a single Gaussian to describe the source
morphology is an oversimplification.

{\bf HXMM20:} Five sources are detected by ALMA, none of which appear to be
lensed.  There are a few faint smudges seen in the {\it HST} image which are
likely to be the rest-frame optical counterparts to the ALMA sources.  The ALMA
sources are all arranged in a chain like shape, possibly suggestive of a larger
filamentary overdensity in which they might reside.  IRAC imaging provides
support for this hypothesis (see Figure~\ref{fig:iraccolor}), as all of the ALMA
sources are detected and have similar mid-IR colors (suggesting they lie at
similar redshift).

@@

{\bf HXMM09:} Two sources are detected by ALMA, both of which are weakly
lensed by a foreground galaxy detected in the {\it HST} image.  An Einstein
radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
results in magnification factors of $\mu_{870} = 2.25 \pm 0.17$ and $\mu_{870}
= 1.48 \pm 0.09$.

@@

{\bf HXMM23:} One source is detected by ALMA, and it is coincident (within the
astrometric uncertainty) with a late-type galaxy seen in the {\it HST} image.
Here, we assume that the {\it HST} source is the true counterpart to the ALMA
source, implying that no lensing is occuring.  Consistent with this hypothesis
is that the SPIRE photometry show blue colors that suggest this object is at low
redshift.

@@

{\bf HXMM12:} One source is detected by ALMA, and it is weakly lensed by a group
of foreground galaxies seen in the {\it HST} image.  We assume an Einstein
radius of $0\farcs2$ for the nearest lensing galaxy and allow a $\pm0\farcs4$
shift in its position relative to that indicated by the {\it HST} image (which
has its astrometry tied to SDSS).  We represent the remaining members of the
group as a single SIS located $4\farcs5$ south and $4\farcs5$ east of the image
centroid and having an Einstein radius of $2\farcs0$.  This is meant to
represent the ``maximal lensing'' scenario, so our measurement of $\mu_{870}$
should be regarded as an upper limit.  The presence of two $3\sigma$ peaks
located near the center of the residual image indicates that the model does not
fit the data perfectly.  This could be an indication that either of our
assumptions for the lens potential or source structure are oversimplifications.
Higher resolution imaging is needed to determine the most likely cause.

{\bf HECDFS12:} This is a complex, very well constrained system.  Two sources
are detected by ALMA: one is strongly lensed and the other is weakly lensed.
In addition, the lens is detected by ALMA (this is one of two sources in the
entire ALMA sample that is unresolved by ALMA).  These facts work together to
provide very tight constraints on the system.  Since the lens is detected by
ALMA, its position relative to the lensed images is unambiguous.  Also, because
there is a strongly lensed source with multiple images, the Einstein radius of
the lens is unambiguous.  A byproduct of these two facts is that the
magnification factor of the weakly lensed source is known to very high
precision as well.  It experiences a magnification factor of $\mu_{870} =
1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
has an Einstein radius of $1.353\pm0.005$).  We use these numbers to inform our
estimates of the Einstein radius for weakly lensed sources without the
excellent contraints provided by this system.  Finally, this source is detected
(and unresolved) in the NRAO VLA Sky Survey \citep{Condon:1998uq}, having
$S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming all of this radio emission
originates from the lens, this implies a spectral slope of $\alpha = -0.24$ and
is consistent with non-thermal emission from the lens.

@@

{\bf HADFS04:} Three sources are detected by ALMA, all of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
multiple images of the ALMA sources.  Based on the brightness of the lens, we
consider to be unlikely values for the Einstein radius that are smaller than
$0\farcs5$, so the results we report for this object should be robust.

{\bf HADFS02:} Two sources are detected by ALMA.  The nearest possible lens is
located $\approx 8\arcsec$ from the ALMA sources, indicating that lensing is
likely to be irrelevant in this system.  The two ALMA sources are similarly
bright ($S_{870} = 8.27 \pm 0.53\,$mJy and $S_{870} = 9.07 \pm 0.27\,$mJy) and
separated by $\approx 0\farcs8$, corresponding to a projected physical distance
of $\approx 6\,$kpc. This distance is typical of the pericentric passage
distance in both hydrodynamical simulations of major mergers
\citep[e.g.,][]{Hayward:2012lr} and CO observations of major mergers
\citep[e.g.,][]{2008ApJ...680..246T, 2010ApJ...724..233E, 2011ApJ...733L..11R,
2011MNRAS.412.1913I}.  Two plausible scenarios are that HADFS02 represents a
major merger that just experienced a first pass or is approaching final
coalescence, either of which significantly enhanced star-formation in the
system.

@@

{\bf HADFS03:} Three sources are detected by ALMA, each of which is weakly
lensed by a bright foreground galaxy seen in the {\it HST} image.  Alternative
scenarios involving strong lensing can be ruled out by the location of the
lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources (the rms
error in the astrometry is set from 2MASS at a level of $\approx 0\farcs4$) as
well as the unusual location and fluxes of the ALMA sources relative to each
other.  We assume an Einstein radius of $0\farcs5$ and fix the position angle
of the lens to be between 40-50 degrees to match the orientation seen in the
{\it HST} image.  Larger Einstein radii can be ruled out by the absence of
counter images north of the lens.

>>>>

%\topmargin -0.0in
\def\boldsymbol{\bf}
\newcommand{\tnm}{\tablenotemark}
\newcommand{\tnt}{\tablenotetext}
\maxdeadcycles=10000

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
    indicates that 36 of the ALMA sources experience a significant flux boost
    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
    and show multiple images.  Combined with our previous work on brighter {\it
    Herschel} sources, the lens models presented here constrain the shape of
    the intrinsic luminosity function for DSFGs to have a break near 8$\,$mJy
    at 880$\,\mu$m with a very steep fall off at higher flux densities.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov Chain Monte Carlo visibility plane analysis tool to
    analyze the source properties.  Nearly 70\% of the {\it Herschel} sources
    break down into multiple ALMA counterparts, consistent with previous
    research indicating that the multiplicity rate is high in bright sources
    discovered in single-dish sub-mm or FIR surveys.  The ALMA counterparts to
    our {\it Herschel} targets are located much closer to each other than ALMA
    counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
    Theoretical models underpredict the excess in number of sources with small
    separations seen in our ALMA sample.  The high multiplicity rate and low
    projected separations between sources seen in our sample argue in favor of
    interactions and mergers plausibly driving both the prodigious emission
    from the brightest DSFGs as well as the sharp downturn above $S_{880} =
    8\,$mJy.

@@

Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimieter
(sub-mm) wavelengths are generally known as dusty star-forming galaxies
(DSFGs).  They cover a wide range in redshift from $z \sim 0.5$ to $z > 6$
\citep{2005ApJ...622..772C, Casey:2012qy, Messias:2014fk, Riechers:2013lr},
with a significant component at $z \sim 2$ \citep{Casey:2012uq,
Bothwell:2013lr}, when they represent the most FIR-luminous objects in
existence during this epoch.   They are signposts of significant over-densities
\citep{Daddi:2009qy, Capak:2011qy} \citep[c.f.][]{Robson:2014xy} and
likely represent the formative stages of the most massive elliptical galaxies
found in the local Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.
Moreover, they constitute an important component of the overall galaxy
population at $z \sim 2$ \citep[e.g.,][]{Magnelli:2011ul}, when the
star-formation rate density in the Universe peaked
\citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.

Our collective understanding of DSFGs is currently taking a dramatic leap
forward thanks in large part to the {\it Herschel Space Observatory}
\citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has revolutized the size and
depth of blind surveys at FIR wavelengths.  In particular, the {\it Herschel}
Multi-tiered Extragalactic Survey \citep[HerMES;][]{Oliver:2012lr} and the {\it
Herschel} Astrophysical Terahertz Large Area Survey
\citep[H-ATLAS;][]{2010PASP..122..499E} together have surveyed $\approx
650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m to the confusion
limit of {\it Herschel} \citep[$\sigma \approx 6-7\,$mJy in each
band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a level
approximately double the confusion limit.  A similar effort to survey large
areas of the sky has been undertaken at longer wavelengths by the South Pole
Telescope \citep[SPT;][]{Carlstrom:2011qy} and the Atacama Cosmology Telescope
\citep{Swetz:2011qy}.

@@

\caption{ {\it Herschel}/SPIRE photometry of all galaxies in the H-ATLAS
phase~I catalog with S/N$ > 3$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m
(log of number of galaxies shown in grayscale).  The sample of HerMES sources
in this paper are shown with green squares (the ``ALMA sample'').  The very
bright {\it Herschel} DSFGs from \citet{Bussmann:2013lr} (the ``SMA sample'')
are shown by red circles, and the overall sample of candidate lensed {\it
Herschel} DSFGs are highlighted by yellow circles.  Lensed SMGs discovered by
the SPT that have published lens models are represented by cyan stars
\citep{Hezaveh:2013fk}.  A magenta diamond shows the location in this diagram
of the stacked signal from ALESS DSFGs.  Representative error bars are shown in
the lower left corner.  The ALMA sample fills the gap in 500$\,\mu$m flux
density space between SMA/SPT and ALESS samples.} \label{fig:sample}

@@

ALMA data were obtained during Cycle~0 over the from 2012 June to 2012 December
(Program 2011.0.00539.S; PI: D. Riechers).  The observations were carried out
in good 870$\,\mu$m weather conditions which resulted in typical system
temperatures of $T_{\rm sys} \sim 130\,$K and phase fluctuations of $\sim
10\,$deg.  Each target was observed until an rms noise level near the phase
center of $\sigma \approx 0.2\,$mJy was achieved.  This typically required 10
minutes of on-source integration time.  For the observations targeting the
CDFS, ELAISS, and COSMOS fields, the data reach $\sigma \approx 0.14\,$mJy.
The number of antennas used varied from 15 to 25.  The antennas were configured
with baseline lengths of 20$\,$m to 400$\,$m, providing a synthesized beamsize
of $\approx 0\farcs5 \times 0\farcs4$ FWHM while ensuring that no flux was
resolved out by the interferometer (since our targets all have size scales
smaller than $1-2 \arcsec$.  When possible, track-sharing of multiple targets
in a single track was used to optimize the {\it uv} coverage.

@@

All observations were conducted with the correlator in ``Frequency Domain
Mode'', providing a total usable bandwidth of 7.5$\,$GHz with spectral windows
centered on 335.995$\,$GHz, 337.995$\,$GHz, 345.995$\,$GHz, 347.996$\,$GHz.  We
searched for evidence of serendipitous spectral lines but found none (typical
sensitivity is $\sigma \approx 8\,$mJy$\,$beam$^{-1}$ in 15$\,$km$\,$sec$^{-1}$
bins).  Given that our observations cover a total of 217.5$\,$GHz in badwidth,
the lack of lines seems more likely to be due to limited sensitivity than
limited bandwidth.

We used the Common Astronomy Software Applications (CASA, version 4.2.1)
package to investigate the quality of the reduced data provided by the North
American ALMA Science Center (NAASC).  Overall, the quality of the processed
data from the NAASC was very high.  We achieved a significant improvement in
the case of the ADFS and XMM targets by excluding datasets with moderate
$T_{\rm sys}$ and poor phase fluctuations.  For a handful of targets with peak
signal-to-noise ratio (S/N) greater than 20, we obtained a $\approx 10\%$
improvement in S/N by using the CASA {\sc selfcal} task with the clean component
model as input to improve the phase gain corrections.  Finally, we updated the
absolute flux calibration to use the Butler-JPL-Horizons 2012 solar system
models.

@@

Figure~\ref{fig:imaging} presents our ALMA images (colorscale) in comparison to
the {\it Herschel} SPIRE images (black-white contours) originally used to
select the targets and noted in each panel as either 250$\,\mu$m, 350$\,\mu$m,
or 500$\,\mu$m.  Each panel is centered on the phase center of the ALMA
observations of that target and a white circle traces the FWHM of the primary
beam of an ALMA 12$\,$m antenna at 870$\,\mu$m.  All flux density measurements
given in this paper have been corrected for the primary beam by dividing the
total flux density by the primary beam correction factor at the center of the
source.  This is a valid approach because all sources have sizes $< 1\arcsec$,
such that the variation in the primary beam correction factor across the source
is insignificant.  A white dashed box represents the region of each image that
is shown in greater detail in Figure~\ref{fig:uvmodels}.

@@

Optical imaging observations using the Gemini Multi-Object Spectrograph-South
\citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of
the program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
structure at $z<1$ and determine which of the ALMA sources are affected by
gravitational lensing.  Nearly half of the ALMA sources lie in regions with
existing deep optical imaging thanks to the extensive HerMES multi-wavelength
dataset --- these were excluded from our Gemini-S program.  The remaining
targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01,
HADFS11, HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each
of these targets were observed for a total of 9$\,$minutes of on-source
integration time in each of $u$, $g$, $r$, $i$, and $z$.  The observations were
obtained during dark time in with adequate seeing conditions (image quality in
the 85th percentile, corresponding to $\approx 1.1\arcsec$.

@@

\caption{ ALMA 870$\mu$m images (color scale, units of mJy/beam) of HerMES
DSFGs (images have not been corrected for primary beam attenuation).  Contours
(black and white) trace 250$\,\mu$m emission from {\it Herschel}.  The FWHM
size of the ALMA synthesized beam is shown in the lower left corner of each
panel.  A solid white circle shows the FWHM size of the primary beam.  Dashed
squares identify the regions of each image that are shown in greater detail in
Figure~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}

@@

When an intervening galaxy (or group of galaxies) is present along the line of
sight, {\sc uvmcmcfit} accounts for the deflection of light caused by this
structure using a simple ray-tracing routine that is adopted from a Python
routine written by A.~Bolton
\footnote{http://www.physics.utah.edu/$\sim$bolton/python\_lens\_demo/}.  This
represents a significant difference from \citet{Bussmann:2012lr} and
\citet{Bussmann:2013lr}, where we used the publicly available {\sc Gravlens}
software \citep{Keeton:2001lr} to map emission from the source plane to the
image plane for a given lensing mass distribution.  {\sc Gravlens} has a wide
range of lens mass profiles as well as a sophisticated algorithm for mapping
source plane emission to the image plane, but it also comes with a significant
input/output penalty that makes parallel computing prohibitively expensive.
For example, modeling a simple system comprising one lens and one source
typically required 24-48$\,$hours using the old software, whereas the same
system can be modeled in less than one hour with the pure-Python code.  The use
of pure-Python code for tracing the deflection of light rays is a critical
component of making {\sc uvmcmcfit} computationally feasible.

@@

We use uniform priors for all model parameters.  The prior on the position of
the lenses covers $\pm0\farcs6$ ($1\farcs0$) in both RA and Dec, a value that
reflects the 1-$\sigma$ absolute astrometric solution between the ALMA and
optical/near-IR images of $0\farcs2$ ($0\farcs4$) for SDSS-based (2MASS-based)
astrometric calibration.  In section~\ref{sec:objectbyobject}, we discuss the
level of agreement between the astrometry from the images and the astrometry
from the lens modeling on an object-by-object basis.  For $\theta_{\rm E}$, the
prior covers $0\farcs1 - 6\arcsec$.  The axial ratios of the lenses and sources
are restricted to be $q_{\rm lens} > 0.3$ and $q_{\rm s} > 0.2$. No prior is
placed on the position angle of the lens or source.  The intrinsic flux density
for any source is allowed to vary from 0.1$\,$mJy to the total flux density
observed by ALMA (we ensure that the posterior PDF of the intrinsic flux
density shows no signs of preferring a value lower than 0.1$\,$mJy).  The source
position is allowed to vary over any reasonable range necessary to fit the data
(typically, this is $\pm 1-2\arcsec$).  The effective radius is allowed to vary
from $0\farcs01 - 1\farcs5$.

@@

{\bf HXMM07:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy detected in the Gemini-S image.  There is a $\approx
0\farcs5$ offset in the position of the foreground galaxy between the lens
model and the Gemini-S image.  Given the absolute astrometric rms uncertainty
of $0\farcs2$ (based on SDSS), we do not consider this offset to be
significant.  The presence of a handful of $\pm3\sigma$ peaks in the residual
map is likely an indication that our assumption of a single Gaussian to
describe the source morphology is an oversimplification.

{\bf HXMM20:} Five sources are detected by ALMA, none of which appear to be
lensed.  There are a few faint smudges seen in the {\it HST} image which are
likely to be the rest-frame optical counterparts to the ALMA sources.  The ALMA
sources are all arranged in a chain like shape, possibly suggestive of a larger
filamentary overdensity in which they might reside.  IRAC imaging provides
support for this hypothesis (see Figure~\ref{fig:iraccolor}), as all of the ALMA
sources are detected and have similar mid-IR colors.

@@

{\bf HXMM09:} Two sources are detected by ALMA, both of which are weakly
lensed by a single foreground galaxy detected in the {\it HST} image.  An Einstein
radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
results in magnification factors of $\mu_{870} = 2.25 \pm 0.17$ and $\mu_{870}
= 1.48 \pm 0.09$.

@@

{\bf HXMM23:} One source is detected by ALMA, and it is coincident (within the
astrometric uncertainty) with a late-type galaxy seen in the {\it HST} image.
Here, we assume that the {\it HST} source is the true counterpart to the ALMA
source, implying that no lensing is occuring.  Consistent with this hypothesis
is that the SPIRE photometry show blue colors that suggest this object is at low
redshift.  Note that models in which the late-type galaxy is lensing the ALMA
source by a modest amount ($\mu_{870} < 1.2$) cannot be ruled out with the
present data.

@@

{\bf HXMM12:} One source is detected by ALMA, and it is weakly lensed by a
group of foreground galaxies seen in the {\it HST} image.  We assume an
Einstein radius of $0\farcs2$ for the nearest lensing galaxy and allow a
$\pm0\farcs4$ (i.e., 2$\sigma$) shift in its position relative to that
indicated by the {\it HST} image (which has its astrometry tied to SDSS).  We
represent the remaining members of the group as a single SIS located $4\farcs5$
south and $4\farcs5$ east of the image centroid and having an Einstein radius
of $2\farcs0$.  This is meant to represent the ``maximal lensing'' scenario, so
our measurement of $\mu_{870}$ should be regarded as an upper limit.  The
presence of two $3\sigma$ peaks located near the center of the residual image
indicates that the model does not fit the data perfectly.  This could be an
indication that either of our assumptions for the lens potential or source
structure are oversimplifications.  Higher resolution imaging is needed to
determine the most likely cause.

{\bf HECDFS12:} This is a complex, well-constrained system.  Two sources
are detected by ALMA: one is strongly lensed and the other is weakly lensed.
In addition, the lens is detected by ALMA (this is one of two sources in the
entire ALMA sample that is unresolved by ALMA).  These facts work together to
provide very tight constraints on the system.  Since the lens is detected by
ALMA, its position relative to the lensed images is unambiguous.  Also, because
there is a strongly lensed source with multiple images, the Einstein radius of
the lens is unambiguous.  A byproduct of these two facts is that the
magnification factor of the weakly lensed source is known to very high
precision as well.  It experiences a magnification factor of $\mu_{870} =
1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
has an Einstein radius of $1.353\pm0.005$).  We use these numbers to inform our
estimates of the Einstein radius for weakly lensed sources without the
excellent contraints provided by this system.  Finally, this source is detected
(and unresolved) in the NRAO VLA Sky Survey \citep{Condon:1998uq}, having
$S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming all of this radio emission
originates from the lens, this implies a spectral slope of $\alpha = -0.24$ and
is consistent with non-thermal emission from the lens.

@@

{\bf HADFS04:} Three sources are detected by ALMA, all of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
multiple images of the ALMA sources.  Values for the Einstein radius that are
smaller than $0\farcs5$ are unlikely based on the brightness of the lens, so
the results we report for this object should be robust.

{\bf HADFS02:} Two sources are detected by ALMA.  The nearest possible lens is
located $\approx 8\arcsec$ from the ALMA sources, indicating that lensing is
likely to be irrelevant in this system.  The two ALMA sources are similarly
bright ($S_{870} = 8.27 \pm 0.53\,$mJy and $S_{870} = 9.07 \pm 0.27\,$mJy) and
separated by $\approx 0\farcs8$, corresponding to a projected physical distance
of $\approx 6\,$kpc. This distance is typical of the pericentric passage
distance in both hydrodynamical simulations of major mergers
\citep[e.g.,][]{Hayward:2012lr} and observations of major mergers
\citep[e.g.,][]{Ivison:2007qv, 2008ApJ...680..246T, 2010ApJ...724..233E,
2011ApJ...733L..11R, 2011MNRAS.412.1913I}.  Two plausible scenarios are that
HADFS02 represents a major merger that just experienced a first pass or is
approaching final coalescence, either of which significantly enhanced
star-formation in the system.

@@

{\bf HADFS03:} Three sources are detected by ALMA, each of which is weakly
lensed by a single bright foreground galaxy seen in the {\it HST} image.
Alternative scenarios involving strong lensing can be ruled out by the location
of the lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources
(the rms error in the astrometry is set from 2MASS at a level of $\approx
0\farcs4$) as well as the unusual location and fluxes of the ALMA sources
relative to each other.  We assume an Einstein radius of $0\farcs5$ and fix the
position angle of the lens to be between 40-50 degrees to match the orientation
seen in the {\it HST} image.  Larger Einstein radii can be ruled out by the
absence of counter images north of the lens.
